---
title: "User Behavior"
author: "Mingwei(Show) Wu"
date: "1/23/2021"
output: pdf_document
---

# Background
## Data randomly extract 8477 customers and 1048575 values from 2014/11/18 to 2014/12/18 in taobao shopping, including customer_id,items_id,behavior_type,location,items_category.

# Goal
## Generate the model by analysing User-behavior, and reporting the outcome.

# data interpretation
## user_id: randomly int of user
## item_id: item id
## behavior: pv(page view), fav(collection), cart(cart), buy
## item_category: type of category of items

```{r}
library(tidyverse)
library(dplyr)
library(sqldf)
library(scales)
```

```{r}
ub<-read.csv("UserBehavior.csv",skip = 1,header = TRUE,nrow=200000)
```


```{r}
ub<-ub%>%
  rename(id=X1,
         user_id=X2333346,
         item_id=X2520771,
         behavior=pv,
         item_category=X1511561733)

```
```{r}
head(ub)
```

```{r}
ub%>%
  ggplot(aes(behavior))+geom_histogram(stat = 'count', binwidth = 50, color='blue',fill='gray') #histogram to show behavior
```
## conducted data with SQL to check duplicated observations.
```{r}
sqldf("select *, count(*)
      from ub
      group by id,user_id,item_id,behavior,item_category
      having count(user_id) > 1") # none of ob is duplicated
```

```{r}
ub%>%
  group_by(user_id)%>%
  count()%>%
  arrange(desc(n)) # calculates 117081 unique customers buy on the website in 200 thousand observations, and one person frequency is 106 at period time of month.
```

```{r}
ub1<-ub%>%
  group_by(behavior)%>%
  count() #counting the amount of behavior type
ub1
```

```{r}
ub2<-ub1%>%
  ungroup(behavior)%>%
  arrange(n)
ub2 
```
```{r}
ub2<-ub2 %>%
  mutate(behavior = factor(behavior, 
                levels = c("buy","cart","fav","pv")),
              cumulative = cumsum(n),
                midpoint = cumulative - n/2,
                labels = paste0(round((n/ sum(n)) * 100, 1), "%"))
ub2
```
```{r}
ub2%>%
  ggplot(aes(x="",y=n,fill=behavior))+geom_bar(width=1,stat = "identity")+
  coord_polar(theta = "y",start=0)+labs(x="",y="", title="customer behavior on web",fill="behavior")+scale_fill_manual(values = c("yellow", "Red", "Green", "Orange"))+theme_void() #pie chart to show the percentage of customer behavior
```

```{r}
ub1 #page_view is 179831 in 200k observations
```
```{r}
unique(ub["user_id"])%>%
  count()  # unique user amount click on website as 117081 in 200k observations
```
```{r}
PV<-c(179831)
UV<-c(117081)
rate_clicked_person<-PV/UV
page_view<-data.frame(PV,UV,rate_clicked_person)
page_view #page_view is 179831, unique customer amount is 117081, mean of clicked is 1.53% as rate
```

```{r}
cart<-c(10906); fav<-c(4934);buy<-4329
behavior<-c("PV","fav+cart","buy")
quantity<-c(PV,fav+cart,buy)
rate<-c(PV/PV,(fav+cart)/PV,buy/PV)
```
```{r}
rate_shopping<-data.frame(behavior,quantity,rate)
rate_shopping  # only 2.4% of the customer who fished processing of shopping, and 9.0% of page_view is collect goods
```
```{r}
cr<-buy/(fav+cart);percent(cr) #27% as conversation rate between fav+cart and buy
```

```{r}
rate_shopping%>%
  ggplot(aes(behavior,y=rate))+geom_bar(stat="identity",color="blue",fill="white")+coord_flip()+geom_text(aes(label=percent(round(rate,2))))+ggtitle("visualization of conversaion rate")
```

```{r}
vnb<-(PV+cart+fav)-buy;vnb #191342 customer only view the page,including add good to chart, but not buy in 300k observations.
```
```{r}
sqldf("select count(behavior) as total_buy
      from ub
      where behavior ='buy'") #only 4329 as buy amount in 300k observations
```

```{r}
ub%>%
  filter(behavior=="buy")%>%
  group_by(user_id)%>%
  count()%>%
  ungroup()%>%
  summarise(rate_person_buy=mean(n)) #1.08% as the rate of people in buy behavior
```
```{r}
ub%>%
  filter(behavior=="buy")%>%
  group_by(user_id)%>%
  count()%>%
  ungroup()%>%
  summarise(total_person_buy=n())
```

```{r}
ub%>%
  filter(behavior=="buy")%>%
  group_by(user_id)%>%
  count()%>%
  filter(n > 1)%>%
  ungroup()%>%
  summarise(rate_people_morethan_once=n()) #269 people is buy on the website more than once
```

```{r}
269/4007 # only 6.7% people who buy more than once in the time period.
```



```{r}
sqldf("select item_category, count(behavior) as amout_buy
      from ub
      where behavior == 'buy'
      group by item_category
      order by count(behavior) desc limit 10") # top 10 sales
```

```{r}
ub%>%
  filter(behavior=="buy")%>%
  group_by(item_category)%>%
  count()%>%
  arrange(desc(n))%>%
  ggplot(aes(item_category))+geom_histogram(color="white",fill="blue")
```
```{r}
ub%>%
  filter(behavior=="pv")%>%
  group_by(item_id)%>%
  count()%>%
  arrange(desc(n))%>%
  head() #top 6 view of 6 items
```
```{r}
ub%>%
  filter(behavior=="buy")%>%
  group_by(item_id)%>%
  count()%>%
  arrange(desc(n))%>%
  head() # top 6 sales of items
```

```{r}
sqldf(" select a.item_id, a.view, b.buy
      from (
      select item_id, count(*) as view
      from ub
      where behavior ='pv'
      group by item_id
      order by count(*) desc
      limit 6
      ) as a
      join (
      select item_id, count(*) as buy
      from ub
      where behavior ='buy'
      group by item_id
      order by count(*) desc
      limit 6
      ) as b
      on a.item_id=b.item_id") # using SQL to query the relationship between the view and buy. only 1 item was buy.
```

```{r}
view_buy<-sqldf(" select a.item_id, a.view, b.buy
      from (
      select item_id, count(*) as view
      from ub
      where behavior ='pv'
      group by item_id
      order by count(*) desc
      ) as a
      left join (
      select item_id, count(*) as buy
      from ub
      where behavior ='buy'
      group by item_id
      order by count(*) desc
      ) as b
      on a.item_id=b.item_id") #create a data frame between view and buy 
head(view_buy)
```
```{r}
pairs(view_buy) #view the plot between view and buy
```

```{r}
view_buy%>%
  ggplot(aes(view,buy))+geom_point() 
```
```{r}
view_buy%>%
  ggplot(aes(view,buy))+geom_point()+geom_smooth() # graph does not show the linear relationship between view and buy
```

# RFM model
### Since the database miss the date values. we cannot count the intervel of the time for the recent buyer. However, we are counting the frequency of the buyer and set up the standard as 3. The further research, we can add the date values, then combine with the frequecy data frame to build up RFM model. Group our customers into 4 major types and provide the sales strategy.
```{r}
ub%>%
  filter(behavior=="buy")%>%
  group_by(user_id)%>%
  count()%>%
  arrange(desc(n)) # amount 4007 as buy, the most frequency of buyer is 6, then minimum is 1. so we can using 3 as standard for Frequency
```

# Long Tail Theory
```{r}
item_fre<-ub%>%
  filter(behavior=="buy")%>%
  group_by(item_id)%>%
  count()%>%
  arrange(desc(n))
head(item_fre) #after counting we can see the most sales of item only 71 times. the total buy was 4007. 71 is less than 80 which is 20 percentage in 4007.
```